### 2022-12-02 definitions.tex
details

@@

@@

>>>>

\problemx{$k$-resilience problem for WSTS}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an effective set $I$ (with a given basis), a set $J$.}
{$\forall s' \in J ~ (s \rightarrow^* s') \implies \exists s'' \in I ~ s' \rightarrow^{\leq k} s''$ ?\newline}

max des I,J possibles \\

J=tout \\
\problemx{$k$-resilience problem for WSTS}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an effective set $I$ (with a given basis).}
{$\forall s'  ~ (s \rightarrow^* s') \implies \exists s'' \in I ~ s' \rightarrow^{\leq k} s''$ ?\newline}

@@

\begin{remark}
\begin{itemize}
\item J=tout et I=$\uparrow x$ alors resilience = couverture.
\item J=tout et I=$\downarrow x$ alors resilience = accessibilité.
\end{itemize}
\end{remark}

@@

si on enlève effective basis of $post^*$:

### 2022-12-02 proof.tex
details

\begin{theorem}
{\sc $k$-resilience} is decidable for effective WSTS with downward/upward compatibility.
%	with strong monotony.
\end{theorem}

@@

\begin{theorem}
{\sc resilience} is decidable for WSTS with downward/upward compatibility.
\end{theorem}

@@

\begin{theorem}
{\sc $k$-resilience} is undecidable for effective WSTS ???
\end{theorem}

\begin{proof}
totot
\end{proof}

>>>>

\begin{theorem}
{\sc $k$-resilience} is decidable for effective WSTS with downward/strong upward compatibility.
%	with strong monotony.
\end{theorem}

@@

\begin{theorem}
{\sc bounded resilience} and {\sc resilience} is decidable for WSTS with downward/strong upward compatibility.
\end{theorem}

@@
